--- 
title: "My Knowledge Database for Websites"
author: "Joffrey Anthony"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---

# Computer Set-Up

When building projects *efficiently*, you will need different set-ups in order to have everything in your code work properly, *not only on your own machine, but also on other machines, for example of another team-member*.

## Mac Tricks

_Before_ we start with the whole set-up, you will also need to know how to **work more efficiently with your Macbook-Computer**.

_Those "tricks" will be useful for many other programs you will need when working in the field of datascience._ 

### Öffne die Developer-Tools von Google-Chrome

- `command + shift + i`

### Speichern 

- `command + s`

### Speichern Unter

- `shift + option + command + s`

### Finder 

- `command + leerschlag`

### Programm schliessen

- `command + q`

### Neuer Ordner 

- `shift + command + n`

### Tilde Zeichen

Das ist nützlich für shortcuts im Terminal, wenn man das Working Directory festlegt: 

- `option + n`

### Backslash 

Useful for paths within the Directory:

- `option + shift + 7` 

### Screenshot vom Bildschirm

- `command + shift + 3`

### Teil des Bildschirms Screen-Schoten 

- `shift + command + 4`

### Verlauf löschen in Chrome Browser 

- `shift + command + entfernen`

### Verlauf löschen Safari 

- `command + alt + e`

### Bildschirm Aufnahme 

Funktioniert nur, wenn QuickTime Player aktiv ist:  

- `option + command + n`

### Lesezeichen in Google Chrome 

- `command + d`

### Search Console Pop Up 

- `option + command + j`

### Format Kopieren einer Zelle (in Numbers)

- `option + command + c`

### Format übertragen einer Zelle (in Numbers) 

- `option + command + v`

### Switch between Applications on your computer 

- `command + tab`

### Move Forward through Tabs 

- `control + tab`

### Zahl als Exponent 

Geht nur in Pages oder Tablett!: 

- `shift + control + command + „+“-Zeichen WÄHREND man die Zahl mit der Maus markiert` 

Dann ist sie noch „normal“ und nicht tiefgestellt —> also so: zum Beispiel: 2.

### Source-Code einer Webseite aufschalten 

- `Option + CMD + u im Browser drücken`

### Interaktive Code-Ansicht für das Abchecken von Webseiten 

`fn + F12-Taste auf Touch Bar drücken`

### Approximate Symbol `≈` 

- `option + x`

## Virtual Environment 

Because the libraries you work with in your projects will be updated over time (this is generally *bad news*, since this will cause all sorts of dependency problems across your libaries you use), it is crucial to understand that you will need a virtual environment (`venv`). There, you will install all the libraries you need. The **major advantage here, is that you can control the version you install the library**. Furthermore, you can send the `venv` to another computer and the people will download exactly the versions of each library. 

<mark>This allows that **your code will <u>always</u> work, independently of the machine you will use**! There will be no dependency problems anymore, which is a huge win.</mark>. :)

### Create a `venv`

Go to your terminal and plug in the following code:

```
conda create -n YOUR-VENVIRONMENT-NAME-HERE python=3.6
```

### Activate your newly created `venv`

Weirdly though, you also need to activate the environment you created above. Plug in the following code:

```
source activate YOUR-ENVIRONMENT-NAME
```

<mark>**Note that the code above can also be used to activate virtual environments you created in the past**!</mark> =) 

### Install packages

Now that you are in your new `venv`, you can start downloading some packages:

```
python -m pip install SOME-PACKAGES
```

### Overview of packages

To check your packages within your `venv`, simply type:

```
conda list
```

### Overview of every `venv` 

To check all the `venv` I created, simply type:

```
conda env list
```

### Execute any python skript

In order to execute a `Python`-script, you will need to head towards the directory that the `.py`-file is and - then - type in:

```
cd go-to-the-dir-where-your-file-is
python my-script.py
```

### Deactivate the `venv`

After you have completed what you wanted, you will need to shut-down the `venv`. Simply type:

```
conda deactivate
```

### Delete a `venv`

Simply type:

```
conda env remove -n my-new-env
```

## R Markdown

When writing Code, I recommend you to use `.Rmd`-Documents, which will allow you to combine both, text, as well as Code (in R, Python, or any other language of your choice).

Actually, this document is written in `.Rmd`-Files, where I combine the text, with so-called "code-snippets", like the follwing:

```
This is a Code-Snippet
```

When writing Code in `R-Markdown`, it will be useful for you to know when: 

1) to execute code wihtin a code-snippet
2) and where not.

### Hide Source Code

This will be done with `echo = FALSE`:

```{r, echo=FALSE}
1 + 1
```

With figures, you need `fig.show = 'hide'` in R:

```{r, fig.show='hide'}
plot(cars)
```

To hide warning-messages, just use `message = FALSE`:

```{r, message=FALSE}
message("You will not see the message.")
```

### Execute a Code-Chunk without showing any Output

You will get an output, e.g. the code will execute, but you will not show the code.

```{r, include=FALSE}
# any R code here
```

### Do NOT execute a Code-Chunk

If you want to show code for demonstration purposes - like on this Website - 
you will probably want to only show the code, but not execute it. This is also possible with `eval=FALSE`:

```{r, include=FALSE}
# any R code here
```

### RMarkdown- VS. Markdown-Files

- Verwende `<ins></ins>` als HTML, um Texte zu Unterstreichen. 
  - <ins>Achtung</ins>: Der HTML-Tag `<u></u>` geht nicht in `.rm`-files. Lustigerweise funktioniert `<u></u>` jedoch in `.Rmd` (= R Markdown) 😂
  
### Nützliche Hexadecimals

- Hexadecimal code for the left square-bracket = `&#91;` --> Ich muss das so machen mit den eckigen Klammern, weil `[]` wird für Links & Bilder verwendet in `Markdown` 🤪
- Hexadecimal code for the right square-bracket = `&#93;` --> Ich muss das so machen mit den eckigen Klammern, weil `[]` wird für Links & Bilder verwendet in `Markdown` 🤪

## Create a Bookdown-Website

1) Use [this Bookdown-Template](https://github.com/jtr13/bookdown-template) to create an awesome website like this one, you are currently at right now.
2) Follow all [the instruction of this 5 Minutes Youtube-Video](https://www.youtube.com/watch?v=m5D-yoH416Y).

## Show Hidden Files?

- `shift + command + "."-Taste` = Use this shortcut when you are in your `Finder` on your mac, where you can see all your directories. You will see that your Mac hides many files from you that end in `.`, for example a `.gitignore`-file (there are many more other files like this one...).

> Why is this useful?

Because - **if you ever need to change to change to a new computer** - you will need to setup this new computer. Using hidden `.`-Files on your _old_ computer will help you to automate this process.

There is a [Youtube-Tutorial on how to configure your _new_ computer exactly like your _old_ computer](https://www.youtube.com/watch?v=r_MpUP6aKiQ).

## For the Future

- <u>Check out this Github-Repo with many free Open-Source Softwares to use</u>: https://github.com/RunaCapital/awesome-oss-alternatives
